---
title: "MORRIS"
author: "William Morris"
date: "4/16/2019"
output: pdf_document
---
#1.#
```{r}
cat("\014")
adv<-read.csv("Advertising.csv")
plotModel<-lm(Sales~TV,data=adv)
plotLM<-summary(plotModel)
print(plotLM)
plot(adv$TV,adv$Sales,pch=20,col="blue",xlab="TV Overhead",ylab="Sales",main="Sales vs TV")
abline(plotModel,col="red")
```

#2.#
```{r}
cat("\014")
data1<-read.csv("MyData1.csv")
model<-lm(Var3~Var1+Var2,data=data1)
LM<-summary(model)
print(LM)
#############################################
cat("The Residual Standard Error is: ",LM$sigma, "\n")
cat("The coefficient of determination is: ",LM$r.squared,"\n")
cat("The observed standard errors are: ",LM$coefficients[,"Std. Error"],"\n")
#############################################
CI<-confint(model,level=.95)
print(model)
print(CI)
#############################################
newInput<-data.frame(Var1=12.55,Var2=20.32)
alpha=.05
ciMean<-predict(model,newdata=newInput,interval="confidence",level=1-alpha)
ciPred<-predict(model,newdata=newInput,interval="prediction",level=1-alpha)
print(ciMean)
print(ciPred)
```

#3.#
```{r}
cat("\014")
houseData<-read.csv("kc_house_data.csv")
houseData$id<-NULL
houseData$date<-NULL
houseData$sqft_basement<-NULL
houseData$floors<-NULL
model<-lm(data=houseData)
LM<-summary(model)
print(LM)
```

So, the "id" and "date" data were clearly insignificant as they are index data only. "sqft_basement" kept coming up in the summary as a non-numeric argument. I was not able to locate the datum that caused this, so I removed it. "floors" was the only qualitative data that I removed because of its insignificance.

I was happy to leave "sqft_lot" in the model, as it's still 99% significant, even if that's substantially less that many of the other data.
